Working Principles of Proof Assistants and Formalization of some proofs in Agda

### 2025-07-03 Mainpaper/paper.tex
basic outline

\section{Main Content}
Divide into multiple subsections as appropriate. For example:
\subsection{Topic A}
Discuss and explain this sub-topic clearly.

\subsection{Topic B}
Likewise, expand on another subtopic. Include figures, equations, or examples to aid exposition.

\section{Comparative Discussion}
(Optional) If your report compares different approaches, schools of thought, or perspectives, lay that out here.

\section{Applications or Case Studies}
(Optional) Describe practical uses or illustrative examples, if any.

\section{Summary and Conclusion}
Summarize the key points discussed. Mention what the reader should take away, and possibly directions for further reading or study.

% ======== References =========
\bibliographystyle{plain} % Or your preferred style
\bibliography{references}

>>>>

\section{General Architecture of Proof Assistants}

\section{Upon Some Proof Assistants and Comparative Study}
\subsection{Coq}

\subsection{Lean}

\subsection{Isabelle}

\subsection{Agda}

\section{ Agda}

\section{Formalization of Some Proofs}

% ======== References =========
\bibliographystyle{plain} 
\bibliography{references}
